Untitled

### 2024-02-05 MSR.rmd
Update

@@

```{r}
i <- 1000 
N <- 4
X <- runif(i) 
DU <- NULL
for (z in 1:i){
  if (X[z]<=1/N) DU[z]<-1
    else if (X[z]<=2/N) DU[z]<-2  
    else if (X[z]<=3/N) DU[z]<-3
  else DU[z] <- 4 
}
(tabel <- table(DU)/length(DU)) 
barplot(tabel, main="Seragam Diskret")
```

>>>>

install_load("MASS")

@@

```{r}
i <- 1000 
N <- 4
X <- runif(i) 
DU <- NULL
for (z in 1:i){
  if (X[z]<=1/N) DU[z]<-1
    else if (X[z]<=2/N) DU[z]<-2  
    else if (X[z]<=3/N) DU[z]<-3
  else DU[z] <- 4 
}
(tabel <- table(DU)/length(DU)) 
barplot(tabel, main="Seragam Diskret")

i <- 1000 
N <- 4
X <- runif(i)
DU <- as.numeric(cut(X, breaks=c(0, 1/N, 2/N, 3/N, 1),  
include.lowest = T))
(tabel <- table(DU)/length(DU)) 
barplot(tabel, main="Seragam Diskret")
i <- 1000  
N <- 4
X <- runif(i)
DU <- 1 +floor(N*X)
(tabel <- table(DU)/length(DU))  
barplot(tabel, main="Seragam Diskret")
```

## Binomial

![](images/clipboard-3560084147.png){width="490"}

```{r}
#Binomial (5,0.65) 
i <- 1000
n <- 5  
p <- .65
Binom <- NULL  
for (z in 1:i){
  m <- 0
  for (k in 1:n){
    y <- (runif(1) <= p) +0  
    m <- m+y
  }
  Binom[z] <- m 
}
(tabel <- table(Binom)/length(Binom))  
barplot(tabel, main="Binomial")

#Binomial (3,0.5)  
i <- 1000
X <- runif(i)
Binom <- as.numeric(cut(X, breaks=c(0, 1/8, 4/8, 7/8, 1),  
include.lowest = T)) -1
(tabel <- table(Binom)/length(Binom)) 
barplot(tabel, main="Binomial")
```

## Geometrik

![](images/clipboard-2245100121.png){width="519"}

```{r}
set.seed(123)
geom <- rgeom(1000, prob = 0.2)

cat("Geometric Distribution (p = 0.2):\n")
head(geom)
hist(geom)
```

## Binomial Negatif

![](images/clipboard-493136764.png){width="524"}

```{r}
nbinom <- rnbinom(1000, size = 5, prob = 0.3)

cat("\nNegative Binomial Distribution (size = 5, prob = 0.3):\n")
head(nbinom)
hist(nbinom)
```
